A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-26 manuscript.Rmd
pregistering explorative analyses

We than proceeded to show one example of how such rigorous and automated reproducibility workflow may enable other innovations, e.g. preregistration as code.
Complementing a preregistration with code is not unheard of but writing a manuscript with code as an integral dynamic element with mock results based on simulated data offers several advantages over classical preregistration.
PAC lets consumers of a research document (e.g. editors, reviewers, readers) clearly distinguish how analyses were planned and how they were conducted via version control.
On the researchers' side, PAC assures that the analysis can effectively answer the research question, i.e. that the analysis can recover the parameters of interest in simulation and lets them employ their resources efficiently by supporting study design decisions.

@@

PACs come with a challenge though.
In contrast to a reproducible script, which should work on the same data, a PAC must work on different data.
We call the property of code that can run on different inputs from a similar context and produce valid outputs "reusability".
This property is based on reproducibility, but requires the researcher to more carefully write the software [@lanerganSoftwareEngineeringReusable1989] such that it is _build-for-reuse_ [@al-badareenReusableSoftwareComponents2010].
The reproducible workflow we present here is heavily automated and hence promotes reusability.
Increased automation is more and more recognized as a means to improve the research process [@rouderMinimizingMistakesPsychological2019] and therefore this workflow fits well together with other innovations that employ automation, like machine readable hypothesis tests [@lakensImprovingTransparencyFalsifiability2021] or automated data documentation [@arslanHowAutomaticallyDocument2019].
Automated and reusable research projects promises a wide range of applications, among them PAC [possibly submitted as a registered report @nosekRegisteredReports2014; @chambersWhatNextRegistered2019], Direct Replication[@simonsValueDirectReplication2014], fully automated living metanalysis [@elliottLivingSystematicReviews2014], Executable Research Articles [@elifesciencespublicationsELifeLaunchesExecutable2020], and other innovations like the live analysis of born open data [@rouderWhatWhyHow2016; @kekecsRaisingValueResearch2019].<!--AB very nice!!-->

>>>>

We than proceeded to show one example of how such rigorous and automated reproducibility workflow may enable other innovations, e.g. preregistration as code.
Complementing a preregistration with code is not unheard of but writing a manuscript with code as an integral dynamic element with mock results based on simulated data offers several advantages over classical preregistration.
First, PAC is more precise by design without becoming overly verbose and can thus more effectively minimize researcher degrees of freedom.
Second, PAC lets consumers of a research document (e.g. editors, reviewers, readers) clearly distinguish how analyses were planned and how they were conducted via version control because preregistration and final manuscript stem from the same dynamic document.
Third, on the researchers' side, PAC assures that the analysis can effectively answer the research question, i.e. that the analysis can recover the parameters of interest in simulation and lets them employ their resources efficiently by supporting study design decisions.
Fourth, a PAC can incorporate data-dependent decisions.
Researchers can therefore plan for possible data analytic problems without deviation from their preregistration.
However, researchers can also preregister explorative analyses, i.e. explorative factor analysis or machine learning methods but precisely calibrate how much exploration is allowed.
When communicating a finding as explorative, it may make a difference if tens or hundreds of variables were considered.

@@

We realize that PACs are challenging.
Not only is every research question or project is suitable for preregistration but PAC requires more programming expertise than a usual analysis.
In contrast to a reproducible script, which should work on the same data, a PAC must work on different data.
We call the property of code that can run on different inputs from a similar context and produce valid outputs "reusability".
This property is based on reproducibility, but requires the researcher to more carefully write the software [@lanerganSoftwareEngineeringReusable1989] such that it is _build-for-reuse_ [@al-badareenReusableSoftwareComponents2010].
The reproducible workflow we present here is heavily automated and hence promotes reusability.
Increased automation is more and more recognized as a means to improve the research process [@rouderMinimizingMistakesPsychological2019] and therefore this workflow fits well together with other innovations that employ automation, like machine readable hypothesis tests [@lakensImprovingTransparencyFalsifiability2021] or automated data documentation [@arslanHowAutomaticallyDocument2019].
Automated and reusable research projects promises a wide range of applications, among them PAC [possibly submitted as a registered report @nosekRegisteredReports2014; @chambersWhatNextRegistered2019], Direct Replication[@simonsValueDirectReplication2014], fully automated living metanalysis [@elliottLivingSystematicReviews2014], Executable Research Articles [@elifesciencespublicationsELifeLaunchesExecutable2020], and other innovations like the live analysis of born open data [@rouderWhatWhyHow2016; @kekecsRaisingValueResearch2019].<!--AB very nice!!-->
